### 2015-06-29 utils/EXTERNAL_CODES_coupled_with_SPECFEM3D/AxiSEM_for_SPECFEM3D/Manual_coupling_AxiSEM_Specfem3D.tex
Final step of coupling w AxiSEM OK (left to check conindence of sismos) + edit coupling Manual

input_box.txt 
input_box_sem_cart.txt 
32                          # number of AxiSEM mpi processes used in solver  
90. 0.                      # source position (lat lon)  
0.  60.                     # chunk center (lat lon)    
1                           # number of axisem simus depends on moment tensor used  
32                          # number of Specfem3D MPI processes  
/[...]/example_1st_for_validation/MESH                           # Specfem MESH dir
/[...]/example_1st_for_validation/OUTPUT_FILES/DATABASES_MPI     # Specfem databases dir
/[...]/AxiSEM_modif_for_coupling_with_specfem/SOLVER/Tractions/1 # AxiSEM tractions dir

@@

10.         # output sampling in Hz (time step that will use in Specfem3D simu) \newline
710. 1800.  # begin time and end time (s.) \newline

@@

>>>>

input_box.txt
input_box_sem_cart.txt
32                          # number of AxiSEM mpi processes used in solver
90. 0.                      # source position (lat lon)
0.  60.                     # chunk center (lat lon)
1                           # number of axisem simus depends on moment tensor used
32                          # number of Specfem3D MPI processes
/[...]/example_1st_for_validation/MESH                          # Specfem MESH dir
/[...]/example_1st_for_validation/OUTPUT_FILES/DATABASES_MPI    # Specfem databases dir
/[...]/example_1st_for_validation/DATA/AxiSEM_tractions/1       # AxiSEM tractions dir

@@

10.         # = 1/DT, i.e. output sampling in Hz (time step that will use in Specfem3D simu) 
710. 1800.  # begin time and end time (s.)

@@

\noindent Go in 'EXAMPLES/coupling\_with\_EXTERNAL\_CODES/with\_AxiSEM/example\_1st\_for\_validation'

\noindent Check in 'DATA/Par\_file', the lines after the comment "\# time step parameters", these parameters must coincide with the parameters in  'reformat.par' (cf STEP 7) :

\item[\textbullet] NSTEP = 10900 ~~ \# $\Longrightarrow$ cf the two values in the second line of 'reformat.par'. This value equals to : 
$$\ds \dfrac{\hbox{second value} - \hbox{the first}}{\text{DT}} ~~ \left(= \dfrac{\hbox{duration of physical time}}{\text{DT}} \right)$$

\noindent So here, it is : $\ds \dfrac{1800 - 710}{0.1} = 10900$

\item[\textbullet] DT = 0.1 ~~ \# $\Longrightarrow$ the inverse of the first line in 'reformat.par' (which is 1/DT)

\noindent Also check in 'DATA/Par\_file', the lines after the comment "\# to couple with an external code (such as DSM, AxiSEM, or FK)" :

\item[\textbullet] COUPLE\_WITH\_EXTERNAL\_CODE = .true. ~~ \# $\Longrightarrow$ always set it to '.true.' in this case

\item[\textbullet] EXTERNAL\_CODE\_TYPE = 2  ~ \# 1 = DSM, 2 = AxiSEM, 3 = FK ~~ $\Longrightarrow$ always set it to '2' for AxiSEM

\item[\textbullet] TRACTION\_PATH  = ./DATA/AxiSEM\_tractions/1/ ~~   \# $\Longrightarrow$ This is where there are the tractions from AxiSEM (from steps 6 and 7) !! CAUTION : verify that they are in this dir, in the form of files 'proc0000**\_sol\_axisem', etc. !!

\item[\textbullet] MESH\_A\_CHUNK\_OF\_THE\_EARTH  = .true.  ~~  \# $\Longrightarrow$ always set it to '.true.' in this case

\noindent And finally, type : run ./batch\_coupling\_step8\_xspecfem3d.sh
